Paper 2 !DRAFT! Do not circulate!

### 2015-04-22 Articles/Article_EcolEcon_2014/Paper2.Rnw
One spelling change in a comment.

<<CD_finite_diff_calcs, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=6, fig.cap='Solow residual time series.'>>=
# Add a bogus "none" column that we can use for the no-energy case
m_histData <- historicalData
m_histData$none <- 1.0
# Melt the the historical data to put energy in one column
m_histData <- melt(select(m_histData, Year, iGDP, iK, iL, iXp, iXf, iU, none, Country, Source), 
                   measure.vars = c("none", "iXp", "iXf", "iU"),
                   variable.name = "energyType",
                   value.name = "iE")
# Calculate finite difference approximations of time derivatives for output and all factors of production
lag <- 5       # Desired lag for calculations. Set to n for differences across n years.
pad <- "tail"  # Desired padding for NA valuse
fd <- m_histData %>% group_by(Source, Country, energyType) %>% arrange(Year) %>% 
  mutate(dydt = ediff(iGDP, pad=pad, lag=lag) / ediff(Year, pad=pad, lag=lag)) %>%
  mutate(dkdt = ediff(iK, pad=pad,   lag=lag) / ediff(Year, pad=pad, lag=lag)) %>%
  mutate(dldt = ediff(iL, pad=pad,   lag=lag) / ediff(Year, pad=pad, lag=lag)) %>%
  mutate(dedt = ediff(iE, pad=pad,   lag=lag) / ediff(Year, pad=pad, lag=lag))

>>>>

<<CD_finite_diff_calcs, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=6, fig.cap='Solow residual time series.'>>=
# Add a bogus "none" column that we can use for the no-energy case
m_histData <- historicalData
m_histData$none <- 1.0
# Melt the the historical data to put energy in one column
m_histData <- melt(select(m_histData, Year, iGDP, iK, iL, iXp, iXf, iU, none, Country, Source), 
                   measure.vars = c("none", "iXp", "iXf", "iU"),
                   variable.name = "energyType",
                   value.name = "iE")
# Calculate finite difference approximations of time derivatives for output and all factors of production
lag <- 5       # Desired lag for calculations. Set to n for differences across n years.
pad <- "tail"  # Desired padding for NA values
fd <- m_histData %>% group_by(Source, Country, energyType) %>% arrange(Year) %>% 
  mutate(dydt = ediff(iGDP, pad=pad, lag=lag) / ediff(Year, pad=pad, lag=lag)) %>%
  mutate(dkdt = ediff(iK, pad=pad,   lag=lag) / ediff(Year, pad=pad, lag=lag)) %>%
  mutate(dldt = ediff(iL, pad=pad,   lag=lag) / ediff(Year, pad=pad, lag=lag)) %>%
  mutate(dedt = ediff(iE, pad=pad,   lag=lag) / ediff(Year, pad=pad, lag=lag))
